Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-12-04 Markdown Documents/Manuscript.Rmd

>>>>

Visitation data was obtained through the [National Park Service Visitor Use Statistics Portal](https://irma.nps.gov/STATS/). These data are generally collected via car counters, permit information, and concessionaire reporting. Methods of collection vary from park to park. Unit specific information can be found on the National Park Service Visitor Use Statistics Portal. Although collection methods are inconsistent across the sample, all data was taken as reported. We retrieved monthly data for all national park units in the Intermountain and Pacific West regions for years 1980 through 2019. To reduce issues regarding park seasonality, we then subset our data to only the three high season months associated with each park. For example, only Summer (June, July, Aug) data was used for Yellowstone National Park.
